% !TEX root = ../thesis_main.tex
\chapter{Acknowledgments}
\vspace{0.5cm}
I would like to thank many people who helped with and enabled me to do the work described in this thesis:
\begin{itemize}[leftmargin=1cm, rightmargin=1cm]
    \vspace{0.5cm}
\item[$-$]{Professor J\"urgen Hennig for the position at the institute, providing an enabling, professional environment and for the helpful comments and corrections on the thesis.}
\item[$-$]{Professor Jan-Bernd H\"ovener for leading the hyperpolarization group and providing much of the equipment and materials used during the course of this work.}
\item[$-$]{PD Dominik von Elverfeldt for a work environment to build upon and for taking over the lead in times of missing governance.}
\item[$-$]{The people of the medical physics institute with all the experts and specialists in NMR, MRI, hardware, software, IT and organizational questions that have an open ear and that you can always ask for help.}
\item[$-$]{The whole hyperpolarization group for numerous meetings, discussions, lab sessions and sometimes even leisure activities}
\item[$-$]{Stephan Knecht and Tim B\"aumlisberger - we arrived colleagues and left friends.}
\item[$-$]{The neurocenter workshop for exciting excursions into the worlds of electronics and fine mechanics and a helping hand whenever needed.}
\item[$-$]{The swimming and spikeball crew for taking care of the lows you inevitably encounter.}
\item[$-$]{My parents and sisters for everlasting support and understanding in every situation.}
\item[$-$]{Jacquie for giving me the space and time I needed when I was writing this thesis and being there when I wasn't.}
\end{itemize}
